---
title: "CHS Analysis"
date: '`r Sys.Date()`'
output: html_document
---

```{r, message=FALSE, warning=FALSE}
# devtools::install_github("austensen/austensen")
library(austensen)
library(tidyverse)
library(glue)
```

```{r}
chs <- feather::read_feather("../dropbox/capstone/data_clean/chs_uhf34_0309.feather")
```

```{r}
get_models <- function(depvar, change = FALSE) {
  if(change == FALSE) {
    indepvars <- c("gent + nongent", "gent + nongent + insured + age65p + pov + asn + blk + his + forborn")
    fomulas <- glue("{depvar} ~ {indepvars}")
  } else if(change == TRUE) {
    ivar1 <- "gent + nongent"
    ivar2 <- " + insured_chg + age65p_chg + pov_chg + asn_chg + blk_chg + his_chg + forborn_chg"
    ivar3 <- " + insured_lag + age65p_lag + pov_lag + asn_lag + blk_lag + his_lag + forborn_lag"
    indepvars <- c(ivar1, collapse(c(ivar1, ivar2)), collapse(c(ivar1, ivar2, ivar3)))
    fomulas <- glue("{depvar} ~ {indepvars}")
  }
  
  map(fomulas, ~ lm(.x, data = chs))
}
```

---

### `gent` & `nongent`:

Share of the UHF34's residents living in gentrifying and non-gentrifying ZCTAs

---

### `good_health`:

Self-reported general health status: 

1 = "Excellent", "Very Good", or "Good"

0 = "Fair" or "Poor"

---

### `gen_health`:

Self-reported general health status: 

5 = "Excellent"

4 = "Very Good" 

3 = "Good"

2 = "Fair" 

1 = "Poor"

---

### `has_pcp`:

> Do you have one person or more than one person you think of as your personal doctor or health care provider?

1 = "Yes"

1 = "No"

---

### `no_care`:

> Was there a time in the past 12 months when you needed medical care, but did not get it?

1 = "Yes"

1 = "No"

---

## Cross-section 2009

```{r, results='asis', warning=FALSE}
c(get_models("gen_health"), 
  get_models("good_health"),
  get_models("has_pcp"),
  get_models("no_care")
  ) %>% 
  stargazer_mod(type = "html")
```


## Changes 2003-2009

```{r, results='asis', warning=FALSE}
c(get_models("gen_health_chg", change = TRUE), 
  get_models("good_health_chg", change = TRUE),
  get_models("has_pcp_chg", change = TRUE)
  ) %>% 
  stargazer_mod(type = "html")
```
